A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-04 paper.tex
caption for Fig 17

\caption{Comparison of power on lineups with different fitted value distributions for conventional tests and visual tests. Power curves of conventional tests for non-linearity and heteroskedasticity patterns are produced by RESET tests and Breusch-Pagan tests respectively. Power curves of visual tests are estimated using five evaluations on each lineup. For lineups with uniform fitted value distribution, the five evaluations are randomly sampled from the total eleven evaluations. The sampling process has been repeated for 500 times and the corresponding power curves are drawn with transparent grey lines. The fitted value distribution has greater impact on the power of conventional tests than visual tests. Meanwhile, uneven distributions including normal and lognormal distributions genearlly produce lower power.}\label{fig:different-x-dist-poly-power}
\end{figure}

>>>>

\caption{Comparison of power on lineups with different fitted value distributions for conventional and visual tests for non-linearity and heteroskedasticity patterns. The power curves of conventional tests for non-linearity and heteroskedasticity patterns are produced by RESET tests and Breusch-Pagan tests, respectively. Power curves of visual tests are estimated using five evaluations on each lineup. For lineups with a uniform fitted value distribution, the five evaluations are repeatedly sampled from the total eleven evaluations to give multiple power curves (grey). Surprisingly, the fitted value distribution has produces more variability in the power of conventional tests than visual tests. Uneven distributions, normal and lognormal distributions, tend to yield lower power.}\label{fig:different-x-dist-poly-power}
\end{figure}
